\bf\mftitle

### 2011-01-31 doc/jInfer/architecture/architecture.tex
Documentation: Architecture: fixing TODOs.

For even more generality in design, we decided to implement abstract classes in midlevel:
\begin{itemize}
	\item \code{AbstractNamedNode} which implements methods from \code{NamedNode} interface to handle context, name and metadata (will discuss later in section \ref{section_metadata}),
	\item \code{AbstractStructuralNode} which implements only the task of deciding if instance is \code{Element} or \code{SimpleData}.
\end{itemize}
% TODO vektor Na jednej strane nas zaujima struktura, na to tam mame isElement() isSimpleData(), na druhej strane nas zaujimaju textove data, na to tam mame getContent() v SD aj atribute.

@@

% TODO vito Aby bolo mozne odkazovat sa na uz zmergovane stavy, ktore sa uz volaju inak, pouzivame mapu premenovani.
Lets take example automaton of fig. \ref{automaton_merge1} (states are labeled [name|finalCount], steps by \{symbol|useCount\}).
One asks to merge states 3 and 4.
State 3 then becomes final state with loop and state 4 disappears (fig. \ref{automaton_merge2}).
If then one asks to merge states 2 and 4, automaton properly handles situation by knowing, that old state 4, was merged into state 3, and merges states 2 and 3 (see fig. \ref{automaton_merge3}).
This can be useful in $k,h-context$ and $s,k-strings$ implementations (find all context/strings, then supply list of states to merge and don't bother with state names updates).

@@

At the moment, only one capability is defined to be communicated across modules, more specifically between \jmodule{IGGenerator} and \jmodule{Simplifier}. This is \code{Capabilities.CAN\_HANDLE\_COMPLEX\_REGEXPS} meaning whether the \code{Simplifier} accepts more complicated regular expressions than simple concatenations of tokens on its input.
% TODO vektor check later - didn't this change?!?

>>>>

For even more generality in design, we decided to implement abstract classes in midlevel:
\begin{itemize}
	\item \code{AbstractNamedNode} which implements methods from \code{NamedNode} interface to handle context, name and metadata (will discuss later in section \ref{section_metadata}),
	\item \code{AbstractStructuralNode} which implements only the task of deciding if instance is \code{Element} or \code{SimpleData}.
\end{itemize}
On the one hand, we are interested in the XML structure - for this reason we use \code{isElement()} and \code{isSimpleData()} of \code{AbstractStructuralNode}. On the other hand, we want to access textual content and its type, for this reason we use \code{getContent()} and \code{getContentType()} of \code{ContentNode}.

@@

To be able to refer to states that have already been merged (and thus have a different name), we use a map of renamings.
Lets take example automaton of fig. \ref{automaton_merge1} (states are labeled [name|finalCount], steps by \{symbol|useCount\}).
One asks to merge states 3 and 4.
State 3 then becomes final state with loop and state 4 disappears (fig. \ref{automaton_merge2}).
If then one asks to merge states 2 and 4, automaton properly handles situation by knowing, that old state 4, was merged into state 3, and merges states 2 and 3 (see fig. \ref{automaton_merge3}).
This can be useful in $k,h-context$ and $s,k-strings$ implementations (find all context/strings, then supply list of states to merge and don't bother with state names updates).

@@

At the moment, only one capability is defined to be communicated across modules, more specifically between \jmodule{IGGenerator} and \jmodule{Simplifier}. This is \code{Capabilities.CAN\_HANDLE\_COMPLEX\_REGEXPS} meaning whether the \code{Simplifier} accepts more complicated regular expressions than simple concatenations of tokens on its input.
